### 2016-12-20 results.tex
still doing a pass...

The set-membership data structure given on the right-hand side of
Figure~\ref{fig:lin-and-bi-lin}, which we call the \emph{bigram
linear-PRF} construction \jnote{Really a bad name\ldots}, was
suggested as a way to allow for privacy-preserving
linkage of medical records~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
\jnote{We should really give more discussion, explaining what the
data structure does in words, and also discussing the goal of
``privacy-preserving record linkage'' and describing the protocol
for doing so (at a high level).} We only address the privacy of this
construction, as the correctness follows immediately from the
correctness of the linear PRF-hash construction. \jnote{Actually, it
seems worth giving a proof of correctness just to get the parameters
right.}

@@

Formally, consider sets of strings over $\bool$, and fix the leakage
function $\leak_{\mathsf{abl}}$ defined by
\[\leak_{\mathsf{abl}}(\{x_1, \ldots, x_n\}) = \{x_1, \ldots, x_{n-1},
x'_n\},\] where $x_n$ is the lexicographically last string in the
given set, and $x'_n$ is equal to $x_n$ with the last bit removed.
Define an attacker $A$ as follows: it chooses a uniform bit~$b$; if
$b=0$ then it outputs the set $S=\{1,111\}$, and if $b=1$ then it
outputs the set $S=\{1, 101\}$. Next, given public information $\pub
= \langle M_1, M_2 \rangle$ (where $M_2$ is the array with more bits
set to~1), it counts the number of positions set to~1 in $M_2$ that
are not set to~1 in~$M_1$. If this number is strictly greater
than~$k$, then $A$ outputs~1; otherwise, it outputs~0.

@@

Now, when $b=0$ the bigram set for the second string contains
exactly one more element than the bigram set for the first string,
and so the number of positions set to~1 in $M_2$ that are \emph{not}
set to~1 in $M_1$ is at most~$k$. On the other hand, when $b=1$ the
bigram set for the second string contains exactly two more elements
than the bigram set for the first string, and so with high
probability the number of positions set to~1 in $M_2$ that are not
set to~1 in $M_1$ exceeds~$k$. (Specifically, in the worst case
there are $2k$ positions---call them~$I$---set to~1 in $M_1$, and
then the number in question exceeds~$k$ as long as a strict majority
of the $2k$ positions set to~1 by the extra bigrams $10, 01$ lie
outside of~$I$. Pairwise independence of those $2k$ positions can be
used to bound this probability. If $k\geq 4$ and $2k/m \leq 1/4$,
this probability is at least %JK

 implies that this happens except with
probability at most $(4 \cdot (\frac{1}{2}- \leq 1/2$.)

%\begin{theorem}%[{\rm SS-privacy of bigram linear-PRF}]
%\label{thm:bi-lin-ss}
%Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for
%integer $\alpha \gg 1$, and let, $k = \lceil \ln(2) \alpha
%\rceil$.\footnote{This value of~$k$ is from the classical analysis
%for minimizing the FP rate for a Bloom filter, and is set this way
%for compatibility with classical results.  It isn't used in any
%essential way in the proof sketch.}  Let~$A$ be the adversary in
%Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the
%advantage
%$\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be
%made arbitrarily close to $1/2$ by choice of~$\alpha$.
%\end{theorem}
\begin{proof}%\tsnote{still a bit sketchy but believable}
On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab'
as input.  It can perfectly simulate $M_1,M_2$ by lazily sampling
random function~$\rho$ itself.  However, it has no information about
the bit~$z$, so at best it can cause~$A$ to output 1 with
probability~$1/2$.  That is
$\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$. \hfill\qed
\end{proof}

@@

\begin{figure}[tp]
\centering
\fpage{0.75}{
\hpagess{.5}{.45}{
\algorithmv{$\Rep(S)$}\\
$\pubaux \gets \emptystring$, $K \getsr \calK$\\
for each $x \in S$\\
\nudge $M_x \gets 0^m$\\
\nudge $B_x \gets \mathsf{bigram}(x)$\\
\nudge for each $b \in B_x$\\
\nudge\nudge for $j \in [k]$\\
\nudge\nudge\nudge $i \gets F_{K}(\langle j, b\rangle) \bmod m$\\
\nudge\nudge\nudge $M_x[i] \gets 1$\\
\nudge $\pubaux \gets \langle\pubaux, M_x \rangle$\\
$\privaux \gets K$\\
Return $(\pubaux,\privaux)$\\
}
{
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$B \gets \mathsf{bigram}(x)$\\
$\overline{M} \gets 0^m$\\
for each $b \in B$\\
\nudge for $j \in [k]$\\
\nudge\nudge $i \gets F_{K}(\langle j,b \rangle) \bmod m$\\
\nudge\nudge $\overline{M}[i] \gets 1$\\
if $\overline{M} \in \pubaux$ then Return 1 \\
Return 0
}
}
\caption{Bigram domain-separated PRF-hash.}
\label{fig:DS-bigram}
\end{figure}

Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} suggest
replacing the linear-PRF hash functions in the previous construction
with independently keyed PRFs as a countermeasure to their attack.
In terms of SS-privacy, however, this change offers no help.  The
following theorem is proved via a nearly identical argument as
Theorem~\ref{thm:bi-lin-ss}.

\begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
structure described in Figure~\ref{fig:DS-bigram}. Let $\leak$ be
the leakage function described just prior to
Theorem~\ref{thm:bi-lin-ss}. Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let
$n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let $k = \lceil
\ln(2) \alpha \rceil$.\footnote{As before, this value of~$k$ is from the
classical analysis for minimizing the FP rate for a Bloom filter,
and is set this way for compatibility with classical results.  It
isn't used in any essential way in the proof sketch.}  Let~$A$ be
the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any
simulator $\Sim$, the advantage
$\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made
arbitrarily close to $1/2$ by choice of~$\alpha$.
\end{theorem}

On the other hand, we can show that this data structure \emph{is}
secure with respect to a different leakage function, namely, one
that leaks the sizes of the intersections of the various bigram
sets. Specifically, for a set $S$ define ${\sf leak}_\cap(S)$ via
the following algorithm:

\begin{figure}[h]
\centering
\fpage{0.5}{
\algorithmv{${\sf leak}_\cap(S)$}\\
$L \gets \emptystring$\\
for each $x \in S$\\
\nudge $B_x \gets \mathsf{bigram}(x)$\\
for each $S' \subseteq S$\\
\nudge $L \gets \left\langle L, \; \left| \bigcap_{x \in S'} B_x \right| \right\rangle$\\
Return $L$}
%\caption{Bigram domain-separated PRF-hash.}
\end{figure}

@@

\begin{figure}[tp]
\centering
\hfpagess{.45}{.45}
{
\adversaryv{$A_{\mathrm{ss}}^{\TestOracle,H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $\ell=1$ to $\binom{m}{k}$\\
\nudge $i_1,i_2,\ldots,i_k \gets \mathcal{I}_\ell$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
{
\adversaryv{$A_{\mathrm{ow}}^{H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $x \in X_1,X_2,\ldots,X_{q-1}$\\
\nudge for $j=1$ to $k$ \\
\nudge \nudge \nudge $i_j \gets H(j,x)$\\
\nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $x' = x$ then Return $x$\\
Return~$X_{q}$
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{{\bf Left:} Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.  The sequence $X_1,X_2,\ldots,X_q,$ are the~$q$ most probable points in the support of~$\distr{}{}$ in decreasing order.  }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{CCS:DonCheWen13} introduce a set-membership
data structure called a \emph{garbled Bloom filter} (GBF).   Modulo
some implementation details, a GBF is like a classical Bloom filter,
but rather than storing a bit 1 at the indices determined by
$H_j(x)$, the GBF stores xor-shares of~$x$.  Thus, if $x \in S$,
then hashing~$x$ and xoring together the strings stored at the
indicated positions recovers~$x$. We give the pseudocode for the GBF
$\Rep$ and $\Qry$ algorithms in Figure~\ref{fig:gbf}.

In~\cite{dong2013private} the GBF is a central piece of a private set-intersection
scheme, in which the client computes a classical BF over its
set~$S_1$, the server computes a GBF over its set~$S_2$, and then an
oblivious transfer protocol is carried out, at the end of which the
client obtains a GBF for $S_1 \cap S_2$ (the server learns nothing).
The authors note that the GBF is a new set-membership data structure
that may be of general interest, so we explore its correctness and
privacy with respect to use case that may or may not make the
representation~$M$ public. The pseudocode in Figure~\ref{fig:gbf}
covers both possibilities.

\heading{Correctness.}
We note that~\cite{dong2013private} provides error-rate analysis, i.e., the
probability of finding a single false-positive in a non-adaptive
attack.  When $\lambda$ is the bit-length of the xor-shares, they
argue that the error-rate is at most $2^{-\lambda}$, roughly because
the xor-shares stored in~$M$ are random strings.  (Note that
  this is independent of~$k,m,n$; although $k>1$ is required for the
  xor shares.)  However, this analysis implicitly assumes that the potential false-positive string~$x$ is fixed
\emph{before}~$M$ is determined.  We will see that this carries over
 to the case in which~$M$ is private (i.e.,
$\pubaux=\emptystring,\privaux=\langle M \rangle$), but when~$M$ is
public things are different.

@@

Now, this adversary will find a false positive, if there is one, but in the worst case it will consider
$\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
and~$k$ are large this is infeasible.  In~\cite{dong2013private} they suggest to
set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
set-membership query would be prohibitive in many applications, and a
$2^{-80}$ false-positive rate would be typically considered overkill in
practice.\footnote{Note
that, as described in~\cite{dong2013private}, $\lambda$ must be at least the
bit-length of the longest element $x \in S$. In practice, this could be
  handled with a slight change to the set membership test, by checking
if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
of~$x$.}
Let us consider a practically interesting set of parameters. Say you have a 1000-position
filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
functions (a la Squid~\cite{fan2000summary}).  This results in a false-positive rate of
approximately 1\% in a classical BF.  There are roughly $2^{35}$
subsets of four indices to consider, which is reasonable on a
commodity laptop.  Moreover, with $n=100$ the expected
number of trials is roughly $2^{28}$.
Note that the attack is easily extended to find $r>1$ false positives.

>>>>

The set-membership data structure given on the right-hand side of
Figure~\ref{fig:lin-and-bi-lin}, which we call the \emph{bigram
linear-PRF} construction \jnote{Really a bad name\ldots}, was
suggested as a way to allow for privacy-preserving linkage of
medical records~\cite{schnell2011novel}. \jnote{We should really
give more discussion, explaining what the data structure does in
words, and also discussing the goal of ``privacy-preserving record
linkage'' and describing the protocol for doing so (at a high
level).} We only address the privacy of this construction, as the
correctness follows immediately from the correctness of the linear
PRF-hash construction. \jnote{Actually, it seems worth giving a
proof of correctness just to get the parameters right.}

@@

Formally, consider sets of strings over $\bool$, and fix the
``all-but-last'' leakage function $\leak_{\mathsf{abl}}$ defined by
\[\leak_{\mathsf{abl}}(\{x_1, \ldots, x_n\}) = \{x_1, \ldots, x_{n-1}\},\]
where $x_n$ is the lexicographically last string in the given set.
\jnote{Could also give all-but-the-2nd bit of $x_n$, but does it
matter?} Define an attacker $A$ as follows: it chooses a uniform
bit~$b$; if $b=0$ then it outputs the set $S=\{1,111\}$, and if
$b=1$ then it outputs the set $S=\{1, 101\}$. Next, given public
information $\pub = \langle M_1, M_2 \rangle$ (where $M_2$ is the
array with more bits set to~1), it counts the number of positions
set to~1 in $M_2$ that are \emph{not} set to~1 in~$M_1$. If $b=0$
and this number is $k$ or less, or if $b=1$ and this number if
strictly greater than~$k$, then $A$ outputs~1; otherwise, it
outputs~0.

@@

Now, when $b=0$ the bigram set for the second string contains
exactly one more element than the bigram set for the first string,
and so the number of positions set to~1 in $M_2$ that are \emph{not}
set to~1 in $M_1$ is at most~$k$. On the other hand, when $b=1$ the
bigram set for the second string contains exactly two more elements
than the bigram set for the first string, and so with high
probability there are more than $k$ positions set to~1 in $M_2$ that
are not set to~1 in~$M_1$. (Specifically, in the worst case there
are $2k$ positions---call them~$I$---set to~1 in $M_1$, and then the
number in question exceeds~$k$ as long as a strict majority of the
$2k$ positions set to~1 by the additional bigrams $10, 01$ lie
outside of~$I$. Pairwise independence of those $2k$ positions can be
used to bound this probability. If $k\geq 4$ and $2k/m \leq 1/4$,
this probability is at least~$1/2$.) \jnote{Check my math? Get
tighter analysis?} We conclude that in the real experiment $A$
outputs~1 with probability at least~3/4.

On the other hand, a simulator~$\Sim$ given ${\sf
leak}_{\mathsf{abl}}(S) = \{1\}$ has no information about~$b$, and
it is not hard to see that no $\Sim$ can cause $A$ to output~1 with
probability better than~1/2.

%\begin{theorem}%[{\rm SS-privacy of bigram linear-PRF}]
%\label{thm:bi-lin-ss}
%Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for
%integer $\alpha \gg 1$, and let, $k = \lceil \ln(2) \alpha
%\rceil$.\footnote{This value of~$k$ is from the classical analysis
%for minimizing the FP rate for a Bloom filter, and is set this way
%for compatibility with classical results.  It isn't used in any
%essential way in the proof sketch.}  Let~$A$ be the adversary in
%Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the
%advantage
%$\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be
%made arbitrarily close to $1/2$ by choice of~$\alpha$.
%\end{theorem}
%\begin{proof}%\tsnote{still a bit sketchy but believable}
%\end{proof}

@@

\begin{figure}[tp]
\centering
\fpage{0.75}{
\hpagess{.5}{.45}{
\algorithmv{$\Rep(S)$}\\
$\pubaux \gets \emptystring$, $K \getsr \calK$\\
for each $x \in S$\\
\nudge $M_x \gets 0^m$\\
\nudge $B_x \gets \mathsf{bigram}(x)$\\
\nudge for each $b \in B_x$\\
\nudge\nudge for $j \in [k]$\\
\nudge\nudge\nudge $i \gets F_{K}(\langle j, b\rangle) \bmod m$\\
\nudge\nudge\nudge $M_x[i] \gets 1$\\
\nudge $\pubaux \gets \langle\pubaux, M_x \rangle$\\
$\privaux \gets K$\\
Return $(\pubaux,\privaux)$\\
}
{
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$B \gets \mathsf{bigram}(x)$\\
$\overline{M} \gets 0^m$\\
for each $b \in B$\\
\nudge for $j \in [k]$\\
\nudge\nudge $i \gets F_{K}(\langle j,b \rangle) \bmod m$\\
\nudge\nudge $\overline{M}[i] \gets 1$\\
if $\overline{M} \in \pubaux$ then Return 1 \\
Return 0
}
}
\caption{Bigram domain-separated PRF-hash. \jnote{There must be some better choice of notation to indicate that
the only change is in the way the hash functions are instantiated. (This is a general comment that
applies to the entire paper.)}}
\label{fig:DS-bigram}
\end{figure}

Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} suggest
replacing the hash functions in the previous construction with
independently keyed PRFs as a countermeasure to their attack.
\jnote{We don't even say what their attack is.} In terms of
simulation-based privacy, however, it is not hard to see---using a
similar attack as in the previous section---that this is of little
help.

%\begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
%Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
%structure described in Figure~\ref{fig:DS-bigram}. Let $\leak$ be
%the leakage function described just prior to
%Theorem~\ref{thm:bi-lin-ss}. Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let
%$n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let $k = \lceil
%\ln(2) \alpha \rceil$.\footnote{As before, this value of~$k$ is from the
%classical analysis for minimizing the FP rate for a Bloom filter,
%and is set this way for compatibility with classical results.  It
%isn't used in any essential way in the proof sketch.}  Let~$A$ be
%the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any
%simulator $\Sim$, the advantage
%$\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made
%arbitrarily close to $1/2$ by choice of~$\alpha$.
%\end{theorem}

On the other hand, we can show that this data structure \emph{does}
achieve our notion of simulation-based privacy with respect to a
different leakage function, namely, one that leaks the sizes of the
intersections of the various bigram sets. Specifically, for a set
$S$ define ${\sf leak}_\cap(S)$ via the following algorithm:

\medskip\begin{center}
\algorithmv{${\sf leak}_\cap(S)$}\\
$L \gets \emptystring$\\
for each $x \in S$\\
\nudge $B_x \gets \mathsf{bigram}(x)$\\
for each $S' \subseteq S$\\
\nudge $L \gets \left\langle L, \; \left| \bigcap_{x \in S'} B_x \right| \right\rangle$\\
Return $L$
%\caption{Bigram domain-separated PRF-hash.}
\end{center}

\jnote{Fix indentation.}

\jnote{I ran out of steam at this point\ldots}

@@

\begin{figure}[tp]
\centering
\hfpagess{.45}{.45}
{
\adversaryv{$A_{\mathrm{ss}}^{\TestOracle,H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $\ell=1$ to $\binom{m}{k}$\\
\nudge $i_1,i_2,\ldots,i_k \gets \mathcal{I}_\ell$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
{
\adversaryv{$A_{\mathrm{ow}}^{H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $x \in X_1,X_2,\ldots,X_{q-1}$\\
\nudge for $j=1$ to $k$ \\
\nudge \nudge \nudge $i_j \gets H(j,x)$\\
\nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $x' = x$ then Return $x$\\
Return~$X_{q}$
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{{\bf Left:} Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.  The sequence $X_1,X_2,\ldots,X_q,$ are the~$q$ most probable points in the support of~$\distr{}{}$ in decreasing order.  }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{CCS:DonCheWen13} introduce a set-membership
data structure called a \emph{garbled Bloom filter} (GBF). Roughly,
whereas for each element $x$ in a given input set a classical Bloom
filter would set positions of an array to~1 as determined by
$H_1(x), \ldots, H_k(x)$, a GBF stores a $k$-out-of-$k$
secret-sharing of $x$ in those positions. (Thus, a GBF is an array
of strings rather than an array of bits.) We provide the pseudocode
in Figure~\ref{fig:gbf}.

In~\cite{CCS:DonCheWen13} the GBF is a central piece of a private
set-intersection scheme, in which the client computes a classical BF
over its set~$S_1$, the server computes a GBF over its set~$S_2$,
and then an oblivious transfer protocol is carried out, at the end
of which the client obtains a GBF for $S_1 \cap S_2$ (the server
learns nothing). The authors note that the GBF is a new
set-membership data structure that may be of general interest, so we
explore its correctness and privacy with respect to use case that
may or may not make the representation~$M$ public. The pseudocode in
Figure~\ref{fig:gbf} covers both possibilities.

\heading{Correctness.} We note that~\cite{CCS:DonCheWen13} provides
error-rate analysis, i.e., the probability of finding a single
false-positive in a non-adaptive attack.  When $\lambda$ is the
bit-length of the xor-shares, they argue that the error-rate is at
most $2^{-\lambda}$, roughly because the xor-shares stored in~$M$
are random strings.  (Note that
  this is independent of~$k,m,n$; although $k>1$ is required for the
  xor shares.)  However, this analysis implicitly assumes that the potential false-positive string~$x$ is fixed
\emph{before}~$M$ is determined.  We will see that this carries over
 to the case in which~$M$ is private (i.e.,
$\pubaux=\emptystring,\privaux=\langle M \rangle$), but when~$M$ is
public things are different.

@@

Now, this adversary will find a false positive, if there is one, but
in the worst case it will consider $\binom{m}{k} \approx m^k$
$k$-tuples of positions.  If both~$m$ and~$k$ are large this is
infeasible.  Dong et al.~\cite{CCS:DonCheWen13} suggest to
set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls
per set-membership query would be prohibitive in many applications,
and a $2^{-80}$ false-positive rate would be typically considered
overkill in practice.\footnote{Note that, as described
in~\cite{CCS:DonCheWen13}, $\lambda$ must be at least the bit-length
of the longest element $x \in S$. In practice, this could be
  handled with a slight change to the set membership test, by checking
if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
of~$x$.}
Let us consider a practically interesting set of parameters. Say you have a 1000-position
filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
functions (a la Squid~\cite{fan2000summary}).  This results in a false-positive rate of
approximately 1\% in a classical BF.  There are roughly $2^{35}$
subsets of four indices to consider, which is reasonable on a
commodity laptop.  Moreover, with $n=100$ the expected
number of trials is roughly $2^{28}$.
Note that the attack is easily extended to find $r>1$ false positives.
